Viscous Erosion in Porous Media

### 2018-01-25 docs/methods/erosion_methods.tex
NM
Writing methods paper, section on uniform stress opening angle

\vsp{30}

@@

@@

\subsubsection{The uniform stress geometry}

>>>>

@@

With the vanishing rate understood, we now seek to quantify the limiting shape formed by a single eroding body.

Certain features of this shape can be predicted analytically by appealing to the principal of uniform stress distribution. In particular, consider the angle formed at the front and rear stagnation points. In long time, the stress becomes uniform, in particular in a small vicinity of this front angle in which body curvature can be ignored. Zooming in on the front angle, we can consider the problem of Stokes flow around an infinite wedge of opening angle $\oangle$
\vsp{30}. Exact solutions can be obtained to this problem via separation of variables in polar coordinates \cite{poz1997}.

@@
